Dancing on Water: The Choreography of Sulfur Dioxide Adsorption to Aqueous Surfaces

### 2011-10-24 Article.tex
Final images for the water and so2 equilibrated orientations
merging
Polishing the review responses

\usepackage {amsmath}
\usepackage {setspace}
\usepackage [pdftex]{graphicx}
\usepackage[sort&compress]{achemso}
\usepackage{lineno}

% some formatting tags
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in

@@

\newcommand{\suldiox}{SO$_2$}
\newcommand{\ang}{\,$\textrm{\AA}$}
\newcommand{\angs}{\ang}
\newcommand{\wat}{H$_2$O}

@@

\begin{abstract}
One might expect the high surface tension of water to be a barrier to adsorption of a gas into the liquid phase, but we know that gaseous adsorption on and into a water surface is a common phenomenon on this planet.  What is not commonly known is how an atmospheric gas such as \suldiox~and molecules at the water surface can overcome the barrier created by strong water-water surface bonding interactions.  What this interplay looks like, the distances from the water surface at which these attractive interactions begin, and how they influence the orientational nature of both \suldiox~and surface water molecules is the focus of this computational study.  The results fill a void in the information about this system existing from previous experimental studies by providing information about the dimensional nature of the gas-surface interactions, and the details of how the two species twist and turn orientationally with increased surface interactions.  Classical molecular dynamics have been employed in both equilibrium and steered molecular dynamics (SMD) simulations for \suldiox~at a neat-water surface, and at a surface with high interfacial \suldiox~concentrations.  The results provide new molecular insights for understanding the interaction of this prevalent gas on aerosols and other aqueous surfaces in the environment.
\end{abstract}

>>>>

\usepackage {amsmath}
\usepackage {textcomp}
\usepackage {setspace}
\usepackage [pdftex]{graphicx}
\usepackage[sort&compress]{achemso}
\usepackage{lineno}

\usepackage[
top    = 0.5in,
bottom = 1.0in]{geometry}
%left   = 2.50cm,
%right  = 2.50cm]{geometry}

% some formatting tags
%\oddsidemargin  0.0in
%\evensidemargin 0.0in
%\textwidth      6.5in

@@

\newcommand{\suldiox}{SO$_2$}
\newcommand{\ang}{\,$\textrm{\AA}$}
\newcommand{\angs}{\ang}
\newcommand{\wat}{H$_2$O}
%\newcommand{\deg}{$\,^{\circ}$}

@@

\begin{abstract}
One might expect the high surface tension of water to be a barrier to absorption of a gas into the liquid phase, but we know that gaseous adsorption onto, and subsequent absorption into a water surface is a common phenomenon on this planet.  What is not commonly known is how an atmospheric gas such as \suldiox~and molecules at the water surface can overcome the barrier created by strong water-water surface bonding interactions.  What this interplay looks like, the distances from the water surface at which these attractive interactions begin, and how they influence the orientational nature of both \suldiox~and surface water molecules is the focus of this computational study.  The results fill a void in the information about this system existing from previous experimental studies by providing information about the dimensional nature of the gas-surface interactions, and the details of how the two species twist and turn orientationally with increased surface interactions.  Classical molecular dynamics have been employed in both equilibrium and steered molecular dynamics (SMD) simulations for \suldiox~at a neat-water surface, and at a surface with high interfacial \suldiox~concentrations.  The results provide new molecular insights for understanding the interaction of this prevalent gas on aerosols and other aqueous surfaces in the environment.
\end{abstract}

### 2011-10-24 EquilibratedOrientation.tex
Polishing the review responses

Geometric analyses were performed to characterize the net molecular orientation of \wat~and \suldiox~molecules at different depths from the water surface location. At each distance from the surface location, an orientation profile was created for both the \wat~and \suldiox~molecules. The bivariate orientation distributions for the angles $\theta$ and $\phi$ at various depths were combined to form the intensity plots that show how the molecular orientation distributions change with distance to the surface location. These plots (Figures \ref{fig:water-orientation}, \ref{fig:so2-transit-angles}, and \ref{fig:so2-surface-angles}) allow for a visual interpretation of how the net orientations are affected when moving from the gas phase through the interfacial region and to the surface location, and then further into the aqueous interfacial region and bulk. Both the neat-water, with only a single \suldiox~introduced, and the high-concentration saturated system were analyzed. In the case of the neat-water system, the introduction of a single \suldiox~does not greatly affect molecular orientation of water molecules in the interfacial region. These results of the water orientation are very similar to a neat-water system without any adsorbed solutes (not shown).

The depth profile plots are arranged as a grid of 2D histograms. Each histogram is calculated for all molecules falling within a particular depth in the water interfacial region. The depth of each plot is marked (in \ang) in the upper-right, with the water surface location set at 0\angs, positive depths lie on the gas-phase side of the surface, and negative depths are on the bulk water side. The horizontal axes of each hisogram represent $\theta$ values, and the vertical axes represent $\phi$ values. Areas of low intensity appear in dark blue, and highest intensity in dark red. Regions of the plots where the intensity (coloration) is equally distributed along either the vertical or horizontal axes are considered isotropic in $\phi$ or $\theta$, respectively. Likewise, areas of the plot with high intensity over a small orientational range are considered to exhibit an orientational preference at the given depth. The angle distributions from both simulated slab surfaces were averaged for all the orientation analyses.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/h2o-angles/theta-phi.png}
		\caption{Molecular orientation histograms of \wat~throughout the surface equilibrated systems. The depth (in \angs) of each histogram within the water interface is numbered in the upper-right of each respective plot. The water surface location is set at a position of 0\angs~with negative distance values located in the bulk of the slab, and positive distances towards the gas phase. Each histogram is a bivariate angle distributions for $\theta$ (horizontal axes) and $\phi$ (vertical axes) in both the neat-\wat~system (top) and the saturated system (bottom). Regions of high intensity are dark red, and low intensity are dark blue.}
		\label{fig:water-orientation}
	\end{center}
\end{figure}

>>>>

Geometric analyses were performed to characterize the net molecular orientation of \wat~and \suldiox~molecules at different depths from the water surface location. At each distance from the surface location, an orientation profile was created for both the \wat~and \suldiox~molecules. The bi-variate orientation distributions for the angles $\theta$ and $\phi$ at various depths were combined to form the intensity plots that show how the molecular orientation distributions change with distance to the surface location. These plots (Figures \ref{fig:water-orientation}, \ref{fig:so2-transit-angles}, and \ref{fig:so2-surface-angles}) allow for a visual interpretation of how the net orientations are affected when moving from the gas phase through the interfacial region and to the surface location, and then further into the aqueous interfacial region and bulk. Both the neat-water, with only a single \suldiox~introduced, and the high-concentration saturated system were analyzed. In the case of the neat-water system, the introduction of a single \suldiox~does not greatly affect molecular orientation of water molecules in the interfacial region. These results of the water orientation are very similar to a neat-water system without any adsorbed solutes (not shown).

The depth profile plots are arranged as a grid of 2D histograms. Each histogram is calculated for all molecules falling within a particular depth in the water interfacial region. The depth of each plot is marked (in \ang) in the upper-right, with the water surface location set at 0\angs, positive depths lie on the gas-phase side of the surface, and negative depths are on the bulk water side. The horizontal axes of each histogram represent $\theta$ values, and the vertical axes represent $\phi$ values. Areas of low intensity appear in dark blue, and highest intensity in dark red. Regions of the plots where the intensity (coloration) is equally distributed along either the vertical or horizontal axes are considered isotropic in $\phi$ or $\theta$, respectively. Likewise, areas of the plot with high intensity over a small orientational range are considered to exhibit an orientational preference at the given depth. The angle distributions from both simulated slab surfaces were averaged for all the orientation analyses.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/h2o-angles/theta-phi.png}
		\caption{Molecular orientation histograms of \wat~throughout the surface equilibrated systems. The depth (in \angs) of each histogram within the water interface is numbered in the upper-right of each respective plot. The water surface location is set at a position of 0\angs~with negative distance values located in the bulk of the slab, and positive distances towards the gas phase. Each histogram is a bi-variate angle distributions for $\theta$ (horizontal axes) and $\phi$ (vertical axes) in both the neat-\wat~system (top) and the saturated system (bottom). Regions of high intensity are dark red, and low intensity are dark blue.}
		\label{fig:water-orientation}
	\end{center}
\end{figure}
